\documentclass{ximera}
\title{choice Base useage}

%\input{preamble.tex}% Only add a preamble file if it is actually necessary for the demo/test.
\begin{document}
\begin{abstract}
    basic useage of the choice commands and environments.
\end{abstract}
\maketitle

{{\Huge \bfseries Last Updated: \today}} \\


\section{Basic Usage}
There are three types of choice for answerables, i.e. three different styles of answers that allow students to select from a (supplied) finite list.
Each of these three forms (multipleChoicec environment, selectAll environment, and wordChoice command) then contains the finite selection of provided answers, each instantiated
using the \verb|\choice[#1]{#2}| command, 
which takes the optional argument (\#1) ``correct'' to flag that choice as a correct 
(if no optional argument is given, the choice is assumed to be an incorrect choice), 
and the required argument is the displayed choice text to the student.

There is the multipleChoice environment which only allows students to pick one of the options and check if it is correct. If the student selects
\textit{any} of the choice command items flagged with the ``[correct]'' key, then it should be marked as correct.
There is the selectAll environment which requires the student to select/highly \textit{all} of the choices that are flagged as ``correct'' 
before submitting to get the question marked as correct.
There is the \verb|\wordChoice{#1}| command takes the choices as its argument (same syntax as used in the environments above) 
but displays those choices in a selectable dropdown menu in-line in the middle of text 
(allowing for fill-in-the-blank multiple choice style in the middle of sentences without breaking formating).

\section{Intended Outcome of Test}
Below should be the following:

A multipleChoice environment with the first and third marked choices as correct, and the rest should be incorrect 
(selecting either the first or third choice and hitting submit should be marked as correct, selecting any other should not.) 

A selectAll environment with the second and fourth choices marked correct, and the rest should be incorrect
(selecting both the second and fourth choices then hitting submit should be marked correct, any other combination of any number of choices should 
be marked incorrect).

A sentence ``Here is a sentence with text'' where ``sentence'' is initially a blank dropdown box with a number of choices. 
Only selecting the choice ``sentence'' will mark it as correct.

\section{Start of Test/Demo Area}
\begin{problem}
\begin{multipleChoice}
\choice[correct]{This is choice 1.}
\choice{This is choice 2.}
\choice[correct]{This is choice 3.}
\choice{This is choice 4.}
\end{multipleChoice}
\end{problem}

\begin{problem}

\begin{selectAll}
\choice{This is choice 1.}
\choice[correct]{This is choice 2.}
\choice{This is choice 3.}
\choice[correct]{This is choice 4.}
\end{selectAll}
\end{problem}


Here is a \wordChoice{\choice{phrase}\choice[correct]{sentence}\choice{equation}} with text


\hrulefill


\end{document}