\documentclass{ximera}
\title{Outcome Default List Test Activity}
\date{Last Updated: 6/5/2025}

% List of outcomes that should display where "\displayOutcomes" is used.
\outcome{Answer some questions about some stuff.}
\outcome{Do something productive.}
\outcome{Learn how Questions work maybe.}
\outcome{Maybe other stuff - who knows!}
\input{preamble.tex}
\begin{document}
\begin{abstract}
    A testbed file for Outcomes.
\end{abstract}
\maketitle

\section{Intended Outcome of Test}

In the preamble we use the \verb|\outcome| command to add an outcome, and add a new outcome with each \verb|\outcome| command. 
Then we use the \verb|\displayOutcomes| command to display the outcomes listed in this file.
The command \verb|\displayOutcomes| takes an optional argument to load an outcome file from a different file (if it exists).

So, in the preamble, we used the following commands to populate the outcomes:
\begin{itemize}
    \item \verb|\outcome{Answer some questions about some stuff.} |
    \item \verb|\outcome{Do something productive.} |
    \item \verb|\outcome{Learn how Questions work maybe.} |
    \item \verb|\outcome{Maybe other stuff - who knows!} |
\end{itemize}


The test area should look (approximately) like the following:


Goals for this Section (Hover over me to see!)\\
At the end of this section, students should be able to...
\begin{itemize}
\item Answer some questions about some stuff.
\item Do something productive.
\item Learn how Questions work maybe.
\item Maybe other stuff - who knows!
\end{itemize}
So go forth and learn!



\section{Start of Test/Demo Area}

\displayOutcomes

\section{End of Test/Demo Area}

Some ending text to ensure that there is no unintended output between end of the test/demo and the end of the document.

\end{document}